\section{Introduction (RB, AL)}
At the end of their life, massive stars leave behind some of the most powerful high energy sources in the sky: neutron stars or black holes. The environment around these fascinating objects allows
us to test conditions which often can not be replicated on Earth. Among these systems, pulsar wind nebulae (PWN) are of particular interest. In them, the relativistic plasma wind ejected by the rotating neutron star interacts with the ambient medium. The latter is in most cases composed of the ejecta of the original star explosion. This interaction leads to bright synchrotron and inverse Compton (IC) emission of the wind electrons, producing some of the brightest sources in the sky (electrons and positrons are referred to together as electrons throughout this text).

Modeling the emission of PWN reveals that these systems are able to accelerate particles to very high energies of up to several PeV. The ultimate energy source of this acceleration is rotation of the neutron star which induces a strong electric potential. As neutron stars are highly magnetized and conducting, they act as a unipolar inductor, creating an electric potential between poles and equator. This electromagnetic energy is carried away from the pulsar magnetosphere with the pulsar wind. Where and how it is transformed into kinetic particle energy is a matter of intense research.

In comparison to other sources of relativistic plasma, PWN can be resolved in great detail, as shown in Fig. \ref{fig:rescomp}. Scales close to the gyroradius of the highest energy electrons in this system can be resolved by current radio, optical and X-ray telescopes. Particularly in two systems, the Crab and Vela PWN, the plasma flow can be resolved down to scales of $\approx 10$ light days. These systems provide perfect test beds to study the behaviour of relativistic magnetized plasma, which is thought to be present in other high energy sources as Gamma-Ray Bursts or Active Galactic Nuclei \citep{Berger_2014,Massaro_2015}. The discovery of gamma-ray flares from the Crab PWN revealed very efficient and rapid acceleration of particles in this system. Strong and rapid gamma-ray flares are also observed in GRBs and AGN (see e.g. \citep{Ackermann_2013} and \citep{Aharonian_2009}). It is likely, that common mechanisms, magnetic reconnection or shock acceleration are responsible for the acceleration in all of these systems (see \citep{Kagan_2015} and \citep{Sironi_2015} for recent reviews).

In contrast to the inner region of the Vela PWN, the Crab PWN has been detected across the electromagnetic spectrum. The plasma motion is resolved in space and time with unmatched resolution in this system (see \citep{Hester_2008} and \citep{BuehlerBlandford2013a} for reviews). It has therefore been the target of most theoretical studies of PWN. In particular, relativistic magntohydrodynamic (RMHD) simulations have provided deep insights into the plasma behaviour over the past decades (see e.g.  \citep{Komissarov_2004,Del_Zanna_2006,Porth_2013}). The qualitative behavior of the global plasma flow in these systems is thought to be understood to date. The energy of the wind emitted by the pulsar is concentrated towards the equator. The wind is thought to be highly magnetized and cold (meaning that its thermal energy is much smaller than its magnetic and bulk kinetic energy). Over time, this wind has blown a bubble into the ejecta of the original star explosion. A reverse shock emerges when the pulsar wind first interacts with the surrounding medium, creating an oblate termination surface (see {\cred Fig. \ref{fig:rmhdflow}} in section \ref{sec:rmhd}). Downstream of this termination surface the plasma flows into the equatorial region forming a torus and towards the poles. The latter flow is a result of the magnetic hoop stress and forms the jet observed perpendicular to the torus.

In this article, we will review the status of our current understanding of the plasma flow in PWN and the particle acceleration happening within it. The article is structured as follows: first, we will introduce the RMHD models of PWN in section \ref{sec:rmhd}. We then proceed to discuss the particle acceleration in PWN. In section \ref{sec:wisps} we discuss what can be learned about the particle acceleration from the dynamical structures called ``wisps'' observed in the Crab nebula. Then we proceed to discuss the gamma-ray flares observed in this system in section \ref{sec:flares}. In this context, we will also discuss recent observational and theoretical results of the inner knot of the Crab nebula in section \ref{sec:knot}, which had been proposed as the emission site of the flares. In section \ref{sec:binaries} we will be extend the discussion to binary systems, in which the pulsar wind interacts with the stellar wind from a companion star. The article concludes with a discussion of solved and unsolved problems of our understanding of PWN in section \ref{sec:discussion}.